NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-24 paper/background.tex
update background

\section{Background}

In order to full appreciate the technqiue discussed in this paper, certain background
in neural network and more specifically neural natural language process models are necessary.
In the following paragraphs, we aim to cover the most relevent backgound knowledge.

\shusen{high level NLP comments}

@@

\subsection{Neural Network Model in NLP}

\shusen{neural linguistic models?}

@@

\subsection{Natural Language Inference}
\label{sec:languageInference}
Natural Language Inference(cite?) is an important machine understanding task in NLP.
The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence.
The prediction must fall in one of three catergories: $\{Entailment, Contradiction, Neutral\}$.
$Entailment$ refers to that the textual information of hypothesis is embedded in premise;
$Contradiction$ means the textuals of hypothesis opposes that of premise;
and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.

Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine
the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.

% showing an example??

\shusen{What is the most standard example to illustrate NLI problem?}

>>>>

\section{Background}
The target audiences of the proposed tool is domain experts who develop learning model for natural language processing tasks. Therefore, certain domain specific background knowledge is required to fully understand and appreciate the technique discussed in this paper. In this section, we first explain the natural language inference (NLI) task and how it fit into the grand challenges in NLP. Then, we examine the common architecture characteristics shared by many state-of-the-art neural linguistic models. Finally, we discuss the role the attention plays in the model and why attention is closely tided to model interpretability.

\subsection{Natural Language Inference}
\label{sec:languageInference}
Natural Language Inference~\cite{MacCartney2009} is an important machine understanding task in NLP.
The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence.

\begin{center}
 \begin{tabular}{c | c c c c} 
 \hline
  & sentences & entail & contradict  & neutral \\ [0.5ex] 
 \hline
 premise & Jim ate an apple. &  -  &  -  & - \\ 
 hypothesis & Jim ate fruits. & \checkmark &   &  \\
 hypothesis & Jim ate an banana. &  & \checkmark & \\
 hypothesis & Tom ate an apple &  &  & \checkmark \\
 hypothesis & Jim ate a Fuji apple. &   &  & \checkmark? \\
 \hline
\end{tabular}
\end{center}
\shusen{What is the most standard example to illustrate NLI problem?}
\shusen{high level NLP comments}

The prediction must fall in one of three categories: $\{Entailment, Contradiction, Neutral\}$.
$Entailment$ refers to that the textual information of hypothesis is embedded in premise;
$Contradiction$ means the textual of hypothesis opposes that of premise;
and $Neutral$ implies no conclusion can be made on either $Entailment$ or $Contradiction$.
%
Recently ~\cite{BowmanAngeliPotts2015} proposed a large dataset for this task. We will examine
the decomposable attention model~\cite{parikh2016emnlp} on this dataset with perturbation.

@@

\subsection{Neural Network Model in NLP}
\shusen{neural linguistic models?}

@@

### 2018-03-24 paper/relatedWorks.tex
update background

One of the most studied aread in model interpretability is the explanation of a given prediction.
Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simplier linear model near the prediction of interests).
%
Despite being invaluable for the providing human understandable explanation, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.

>>>>

One of the most studied aread in model interpretability is the explanation of a given prediction.
Many works have been dedicated to providing intuitive explanations for a given prediction, several~\cite{RibeiroSinghGuestrin2016, KrausePererNg2016} of which approach the problem from a model agnostic approach that made them applicable to different applications (i.e., by fitting a simpler linear model near the prediction of interests).
%
Despite being invaluable for the providing human understandable explanation, the lack of the ability to access and explore the internal states of the model, which is vitally important to make sense of why a model fail, limits their ability for more in depth exploration and evaluation of the model.
